---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regexcite

<!-- badges: start -->
<!-- badges: end -->

The goal of regexcite is to make regular expressions more exciting!
It provides convenience functions to make some common tasks with string 
manipulation and regular expressions a bit easier.

## Installation

You can install the development version of regexcite from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("Wendy1907/regexcite")
```

## Usage

A fairly common task when dealing with strings is the need to split a 
single string into many parts.
```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

That's exactly what `regexcite::str_split_one()` does.
```{r}
library(regexcite)

str_split_one(x, pattern = ",")
```

`str_split_one()` is built on `stringr::str_split()`, so you can use 
its `n` argument and stringr's interface for the `pattern`.
```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```
